\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion} 

This report presents our work together within our internship experience performed at \textbf{CNSS (Caisse Nationale de Sécurité Sociale)} as part of our final-year project to obtain the \textbf{\textit{Applied Bachelor's Degree in Business Computing}} at ESEN \textbf{(Higher School of Digital Economy)}.
\vspace{0.5cm}
This semester-long internship is an assignment that every student has to undertake to acclimate to business life and observe how the business world functions by applying everything that is learned throughout the studies. Evidently, all of this would not have been possible without our supervisors guidance.
\vspace{0.5cm}
We were tasked with designing and developing a File Submission platform.
\vspace{0.5cm}
We initially presented the overall context of our internship at CNSS in this report, then presented a first chapter on \textbf{"Project Study"}, where we established the choice of the Agile \textbf{"SCRUM"} approach. This led us to a second chapter, \textbf{"Planning and Architecture"}, where we established our problem statement by outlining requirements and then began to implement SCRUM by establishing the product backlog.
\vspace{0.5cm}
The next three chapters \textbf{"Sprint 1: User and Submitted File Management" , "Sprint 2: Tracking, Notifications and Statistics"} and \textbf{"Sprint 3: User Access and Service Request Foundation"} that were the cornerstone of our project. These chapters included user story specifications, use case diagram schematization, scenario workflow description, use case design, implementation, and testing.
\vspace{0.5cm}
Finally, the last chapter of this report was a \textbf{closure phase}, where we presented the programming languages and tools used in developing our platform.
\vspace{0.5cm}
This was a highly engaging project, as it allowed us to explore the domain of Social Security fund and its needs while boosting our technical knowledge.
\vspace{0.5cm}
Our site, however, does not stay at this point. A series of other capabilities can be introduced, such as cross-posting CNSS services ads on other sites and allowing engaged insured individuals within the \textbf{CNSS} to input Files through the web, which is afterall the main goal of our project digitalizing and automating processes to make life much more easier than before.